Analyzing Housing Affordability in the United States: The Role of Inflation, Interest Rates, and Supply

### 2024-11-25 paper/paper.qmd
finished creating survey

Research focusing on the effectiveness of government programs, such as housing subsidies, rent control, or first-time homebuyer incentives, could provide actionable recommendations for policymakers. Evaluating these interventions in the context of affordability trends would help determine which policies have the most significant impact.

@@

# Model details {#sec-model-details}

## Diagnostics

@@

>>>>

Research focusing on the effectiveness of government programs, such as housing subsidies, rent control, or first-time home buyer incentives, could provide actionable recommendations for policymakers. Evaluating these interventions in the context of affordability trends would help determine which policies have the most significant impact.

@@

## Model Diagnostics {#sec-model-details}

@@

The survey can be found at this link: <https://forms.gle/xLyZsGiEEDcwPnH66>

## Copy of the Survey
